Fast and exact visibility on digitized shapes and application to saliency-aware normal estimation

### 2025-04-23 DGMM2025/paper.tex
adding visuals for visibility example

@@

                    \draw[thick,MyGreen,arrows = {Bracket[sharp]-Bracket[sharp]}] (-0.6,12)--(0.6,12);
                    \draw[thick,gray,arrows = {Bracket[sharp]-Bracket[sharp]}] (-0.6,11.5)--(2.6,11.5);
                    \draw[thick,gray,arrows = {Bracket[sharp]-Bracket[sharp]}] (4.4,11.5)--(10.6,11.5);
                    \draw[thick,violet,arrows = {Bracket[sharp]-Bracket[sharp]}] (-0.6,11)--(1.6,11);
                    \draw[thick,violet,arrows = {Bracket[sharp]-Bracket[sharp]}] (4.4,11)--(9.6,11);
                    \draw[thick,red,arrows = {Bracket[sharp]-Bracket[sharp]}] (-0.6,10.5)--(1.6,10.5);
                    \draw[thick,red,arrows = {Bracket[sharp]-Bracket[sharp]}] (4.4,10.5)--(9.6,10.5);

                    \draw[thick,MyGreen,arrows = {Bracket[sharp]-Bracket[sharp]}] (-0.6,9.5)--(0.6,9.5);
                    \draw[thick,gray,arrows = {Bracket[sharp]-Bracket[sharp]}] (-0.6,9)--(2.6,9);
                    \draw[thick,gray,arrows = {Bracket[sharp]-Bracket[sharp]}] (4.4,9)--(10.6,9);
                    \draw[thick,violet,arrows = {Bracket[sharp]-Bracket[sharp]}] (-0.6,8.5)--(1.6,8.5);
                    \draw[thick,violet,arrows = {Bracket[sharp]-Bracket[sharp]}] (4.4,8.5)--(9.6,8.5);
                    \draw[thick,red,arrows = {Bracket[sharp]-Bracket[sharp]}] (-0.6,8)--(1.6,8);
                    \draw[thick,red,arrows = {Bracket[sharp]-Bracket[sharp]}] (4.4,8)--(9.6,8);

                    \draw[thick,MyGreen,arrows = {Bracket[sharp]-Bracket[sharp]}] (-0.6,7)--(2.6,7);
                    \draw[thick,gray,arrows = {Bracket[sharp]-Bracket[sharp]}] (-0.6,6.5)--(10.6,6.5);
                    \draw[thick,violet,arrows = {Bracket[sharp]-Bracket[sharp]}] (-0.6,6)--(7.6,6);
                    \draw[thick,red,arrows = {Bracket[sharp]-Bracket[sharp]}] (-0.6,5.5)--(1.6,5.5);
                    \draw[thick,red,arrows = {Bracket[sharp]-Bracket[sharp]}] (4.4,5.5)--(7.6,5.5);

                    \draw[thick,black,arrows = {-Stealth[]}] (-0.6,4.5)--(1.4,4.5);
                    \draw[thick,MyGreen,arrows = {Bracket[sharp]-Bracket[sharp]}] (1.4,4.5)--(2.6,4.5);
                    \draw[thick,gray,arrows = {Bracket[sharp]-Bracket[sharp]}] (1.4,4)--(5.6,4);
                    \draw[thick,gray,arrows = {Bracket[sharp]-Bracket[sharp]}] (6.4,4)--(8.6,4);
                    \draw[thick,gray,arrows = {Bracket[sharp]-Bracket[sharp]}] (9.4,4)--(10.6,4);
                    \draw[thick,violet,arrows = {Bracket[sharp]-Bracket[sharp]}] (-0.6,3.5)--(2.6,3.5);
                    \draw[thick,violet,arrows = {Bracket[sharp]-Bracket[sharp]}] (4.4,3.5)--(5.6,3.5);
                    \draw[thick,violet,arrows = {Bracket[sharp]-Bracket[sharp]}] (7.4,3.5)--(7.6,3.5);
                    \draw[thick,red,arrows = {Bracket[sharp]-Bracket[sharp]}] (-0.6,3)--(1.6,3);
                    \draw[thick,red,arrows = {Bracket[sharp]-Bracket[sharp]}] (4.4,3)--(5.6,3);
                    \draw[thick,red,arrows = {Bracket[sharp]-Bracket[sharp]}] (7.4,3)--(7.6,3);

                    \draw[thick,black,arrows = {-Stealth[]}] (-0.6,2)--(1.4,2);
                    \draw[thick,MyGreen,arrows = {Bracket[sharp]-Bracket[sharp]}] (1.4,2)--(2.6,2);
                    \draw[thick,gray,arrows = {Bracket[sharp]-Bracket[sharp]}] (1.4,1.5)--(5.6,1.5);
                    \draw[thick,gray,arrows = {Bracket[sharp]-Bracket[sharp]}] (6.4,1.5)--(8.6,1.5);
                    \draw[thick,gray,arrows = {Bracket[sharp]-Bracket[sharp]}] (9.4,1.5)--(10.6,1.5);
                    \draw[thick,violet,arrows = {Bracket[sharp]-Bracket[sharp]}] (-0.6,1)--(2.6,1);
                    \draw[thick,violet,arrows = {Bracket[sharp]-Bracket[sharp]}] (4.4,1)--(5.6,1);
                    \draw[thick,violet,arrows = {Bracket[sharp]-Bracket[sharp]}] (7.4,1)--(7.6,1);
                    \draw[thick,red,arrows = {Bracket[sharp]-Bracket[sharp]}] (-0.6,0.5)--(1.6,0.5);
                    \draw[thick,red,arrows = {Bracket[sharp]-Bracket[sharp]}] (4.4,0.5)--(5.6,0.5);
                    \draw[thick,red,arrows = {Bracket[sharp]-Bracket[sharp]}] (7.4,0.5)--(7.6,0.5);

                \end{tikzpicture}}
        \end{tabular}
        \caption{Evolution of the visibility check algorithm for a 2,1 vector. Green is the vector lattice map, black is the figure lattice map, red are the current intervals of positions where the visibility is still possible. The last red intervals are the visible positions. We travel the lattice maps from bottom-up. }
        \label{fig:enter-label}
    \end{figure}

@@

@@

@@

    \begin{figure}
      \begin{center}
        \begin{tabular}{|c||c|c|c|} \hline
          Curvature & II normals & CTriv normals & Our normals \\ \hline \hline
          $\kappa_1$&
          \includegraphics[width=0.3\textwidth]{pictures/d20-k1-II}&
          \includegraphics[width=0.3\textwidth]{pictures/d20-k1-CTriv}&
          \includegraphics[width=0.3\textwidth]{pictures/d20-k1-NV}\\ \hline
          $\kappa_2$&
          \includegraphics[width=0.3\textwidth]{pictures/d20-k2-II}&
          \includegraphics[width=0.3\textwidth]{pictures/d20-k2-CTriv}&
          \includegraphics[width=0.3\textwidth]{pictures/d20-k2-NV}\\ \hline
          $H$&
          \includegraphics[width=0.3\textwidth]{pictures/d20-H-II}&
          \includegraphics[width=0.3\textwidth]{pictures/d20-H-CTriv}&
          \includegraphics[width=0.3\textwidth]{pictures/d20-H-NV}\\ \hline
          $G$&
          \includegraphics[width=0.3\textwidth]{pictures/d20-G-II}&
          \includegraphics[width=0.3\textwidth]{pictures/d20-G-CTriv}&
          \includegraphics[width=0.3\textwidth]{pictures/d20-G-NV}\\ \hline
        \end{tabular}
      \end{center}
      \caption{Estimation of curvatures using Corrected Normal Current
        estimators \cite{lachaud:2022-dcg} for the shape ``Dice-20'' of Thingi10K
        database at resolution $256^3$. This estimator is
        parameterized by an input normal estimator: first column by
        ``Integral Invariant normals'' (radius $r=4.77$, second column
        by ``Convolved Trivial normals'' (radius $k=3$), third column
        by our presented normal estimator (radius $r=8.5$). Per row are displayed the
        estimated curvatures in order: first and second principal
        curvatures $\kappa_1$ and $\kappa_2$, mean curvature $H$,
        Gaussian curvature $G$. The range of curvature between deep
        blue and deep red is $\lbrack -0.1, 0.1 \rbrack$ with white
        color equal to $0$.}
    \end{figure}

>>>>

                \draw[red,arrows = {-Stealth[]}] (0,0)--(2,1);
                \draw[red,arrows = {-Stealth[]}] (1,0)--(3,1);
                \draw[red,arrows = {-Stealth[]}] (2,0)--(4,1);
                \draw[red,arrows = {-Stealth[]}] (5,0)--(7,1);
                \draw[red,arrows = {-Stealth[]}] (6,0)--(8,1);
                \draw[red,arrows = {-Stealth[]}] (8,0)--(10,1);

@@

                    \draw[thick,MyGreen,arrows = {Bracket[sharp]-Bracket[sharp]}] (-0.6,12)--(0.6,12);
                    \draw[thick,gray,arrows = {Bracket[sharp]-Bracket[sharp]}] (-0.6,11.5)--(2.6,11.5);
                    \draw[thick,gray,arrows = {Bracket[sharp]-Bracket[sharp]}] (4.4,11.5)--(10.6,11.5);
                    \draw[thick,violet,arrows = {Bracket[sharp]-Bracket[sharp]}] (-0.6,11)--(1.6,11);
                    \draw[thick,violet,arrows = {Bracket[sharp]-Bracket[sharp]}] (4.4,11)--(9.6,11);
                    \draw[thick,red,arrows = {Bracket[sharp]-Bracket[sharp]}] (-0.6,10.5)--(1.6,10.5);
                    \draw[thick,red,arrows = {Bracket[sharp]-Bracket[sharp]}] (4.4,10.5)--(9.6,10.5);
                    \filldraw[black] (-0.5,10.5) circle (0.05);
                    \filldraw[black] (0.5,10.5) circle (0.05);
                    \filldraw[black] (1.5,10.5) circle (0.05);
                    \filldraw[black] (4.5,10.5) circle (0.05);
                    \filldraw[black] (5.5,10.5) circle (0.05);
                    \filldraw[black] (6.5,10.5) circle (0.05);
                    \filldraw[black] (7.5,10.5) circle (0.05);
                    \filldraw[black] (8.5,10.5) circle (0.05);
                    \filldraw[black] (9.5,10.5) circle (0.05);

                    \draw[thick,MyGreen,arrows = {Bracket[sharp]-Bracket[sharp]}] (-0.6,9.5)--(0.6,9.5);
                    \draw[thick,gray,arrows = {Bracket[sharp]-Bracket[sharp]}] (-0.6,9)--(2.6,9);
                    \draw[thick,gray,arrows = {Bracket[sharp]-Bracket[sharp]}] (4.4,9)--(10.6,9);
                    \draw[thick,violet,arrows = {Bracket[sharp]-Bracket[sharp]}] (-0.6,8.5)--(1.6,8.5);
                    \draw[thick,violet,arrows = {Bracket[sharp]-Bracket[sharp]}] (4.4,8.5)--(9.6,8.5);
                    \draw[thick,red,arrows = {Bracket[sharp]-Bracket[sharp]}] (-0.6,8)--(1.6,8);
                    \draw[thick,red,arrows = {Bracket[sharp]-Bracket[sharp]}] (4.4,8)--(9.6,8);
                    \filldraw[black] (-0.5,8) circle (0.05);
                    \filldraw[black] (0.5,8) circle (0.05);
                    \filldraw[black] (1.5,8) circle (0.05);
                    \filldraw[black] (4.5,8) circle (0.05);
                    \filldraw[black] (5.5,8) circle (0.05);
                    \filldraw[black] (6.5,8) circle (0.05);
                    \filldraw[black] (7.5,8) circle (0.05);
                    \filldraw[black] (8.5,8) circle (0.05);
                    \filldraw[black] (9.5,8) circle (0.05);

                    \draw[thick,MyGreen,arrows = {Bracket[sharp]-Bracket[sharp]}] (-0.6,7)--(2.6,7);
                    \draw[thick,gray,arrows = {Bracket[sharp]-Bracket[sharp]}] (-0.6,6.5)--(10.6,6.5);
                    \draw[thick,violet,arrows = {Bracket[sharp]-Bracket[sharp]}] (-0.6,6)--(7.6,6);
                    \draw[thick,red,arrows = {Bracket[sharp]-Bracket[sharp]}] (-0.6,5.5)--(1.6,5.5);
                    \draw[thick,red,arrows = {Bracket[sharp]-Bracket[sharp]}] (4.4,5.5)--(7.6,5.5);
                    \filldraw[black] (-0.5,5.5) circle (0.05);
                    \filldraw[black] (0.5,5.5) circle (0.05);
                    \filldraw[black] (1.5,5.5) circle (0.05);
                    \filldraw[black] (4.5,5.5) circle (0.05);
                    \filldraw[black] (5.5,5.5) circle (0.05);
                    \filldraw[black] (6.5,5.5) circle (0.05);
                    \filldraw[black] (7.5,5.5) circle (0.05);

                    \draw[thick,black,arrows = {-Stealth[]}] (-0.6,4.5)--(1.4,4.5);
                    \draw[thick,MyGreen,arrows = {Bracket[sharp]-Bracket[sharp]}] (1.4,4.5)--(2.6,4.5);
                    \draw[thick,gray,arrows = {Bracket[sharp]-Bracket[sharp]}] (1.4,4)--(5.6,4);
                    \draw[thick,gray,arrows = {Bracket[sharp]-Bracket[sharp]}] (6.4,4)--(8.6,4);
                    \draw[thick,gray,arrows = {Bracket[sharp]-Bracket[sharp]}] (9.4,4)--(10.6,4);
                    \draw[thick,violet,arrows = {Bracket[sharp]-Bracket[sharp]}] (-0.6,3.5)--(2.6,3.5);
                    \draw[thick,violet,arrows = {Bracket[sharp]-Bracket[sharp]}] (4.4,3.5)--(5.6,3.5);
                    \draw[thick,violet,arrows = {Bracket[sharp]-Bracket[sharp]}] (7.4,3.5)--(7.6,3.5);
                    \draw[thick,red,arrows = {Bracket[sharp]-Bracket[sharp]}] (-0.6,3)--(1.6,3);
                    \draw[thick,red,arrows = {Bracket[sharp]-Bracket[sharp]}] (4.4,3)--(5.6,3);
                    \draw[thick,red,arrows = {Bracket[sharp]-Bracket[sharp]}] (7.4,3)--(7.6,3);
                    \filldraw[black] (-0.5,3) circle (0.05);
                    \filldraw[black] (0.5,3) circle (0.05);
                    \filldraw[black] (1.5,3) circle (0.05);
                    \filldraw[black] (4.5,3) circle (0.05);
                    \filldraw[black] (5.5,3) circle (0.05);
                    \filldraw[black] (7.5,3) circle (0.05);

                    \draw[thick,black,arrows = {-Stealth[]}] (-0.6,2)--(1.4,2);
                    \draw[thick,MyGreen,arrows = {Bracket[sharp]-Bracket[sharp]}] (1.4,2)--(2.6,2);
                    \draw[thick,gray,arrows = {Bracket[sharp]-Bracket[sharp]}] (1.4,1.5)--(5.6,1.5);
                    \draw[thick,gray,arrows = {Bracket[sharp]-Bracket[sharp]}] (6.4,1.5)--(8.6,1.5);
                    \draw[thick,gray,arrows = {Bracket[sharp]-Bracket[sharp]}] (9.4,1.5)--(10.6,1.5);
                    \draw[thick,violet,arrows = {Bracket[sharp]-Bracket[sharp]}] (-0.6,1)--(2.6,1);
                    \draw[thick,violet,arrows = {Bracket[sharp]-Bracket[sharp]}] (4.4,1)--(5.6,1);
                    \draw[thick,violet,arrows = {Bracket[sharp]-Bracket[sharp]}] (7.4,1)--(7.6,1);
                    \draw[thick,red,arrows = {Bracket[sharp]-Bracket[sharp]}] (-0.6,0.5)--(1.6,0.5);
                    \draw[thick,red,arrows = {Bracket[sharp]-Bracket[sharp]}] (4.4,0.5)--(5.6,0.5);
                    \draw[thick,red,arrows = {Bracket[sharp]-Bracket[sharp]}] (7.4,0.5)--(7.6,0.5);
                    \filldraw[black] (-0.5,0.5) circle (0.05);
                    \filldraw[black] (0.5,0.5) circle (0.05);
                    \filldraw[black] (1.5,0.5) circle (0.05);
                    \filldraw[black] (4.5,0.5) circle (0.05);
                    \filldraw[black] (5.5,0.5) circle (0.05);
                    \filldraw[black] (7.5,0.5) circle (0.05);

                \end{tikzpicture}}
        \end{tabular}
        \caption{Evolution of the visibility check algorithm for a 2,1 vector. Green is the vector lattice map, black is the figure lattice map, red are the current intervals of positions where the visibility is still possible. The last red intervals are the visible positions. We travel the lattice maps from bottom-up. The found possible visibilities are shown on the original figure}
        \label{fig:enter-label}
    \end{figure}

@@

    In order to compute the visibility, we first compute $\Omega = \text{Star}(C)$. Then for each primal direction of
    coordinates at most $r$, we look at all the possible positions this specific direction does link 2 visible points
    of the cell complex. In order to do so, for each shift in $\Omega$, we compute the positions where points are
    visible using the same method as presented in \ref{fig:enter-label}.

@@

    To efficiently compute the intersection of 2 lists of intervals $K$ and $L$, we go through the first 2 unvisited
    elements of the 2 lists. If they don't overlap (i.e. the start and end of the 1st interval are both smaller than
    the start of the other), then we can discard the smaller interval. Else, we construct the intersection of these
    2 intervals as one of the resulting intervals. We then can skip the interval with the smallest end. If both
    intervals have the same end, then both intervals can be skipped. Doing this computation until one of the lists
    is empty returns the intersection of both lists of intervals.

@@

    \begin{figure}
        \begin{center}
            \begin{tabular}{|c||c|c|c|}
                \hline
                Curvature & II normals & CTriv normals & Our normals \\ \hline \hline
                $\kappa_1$ &
                \includegraphics[width=0.3\textwidth]{pictures/d20-k1-II} &
                \includegraphics[width=0.3\textwidth]{pictures/d20-k1-CTriv}&
                \includegraphics[width=0.3\textwidth]{pictures/d20-k1-NV}\\ \hline
                $\kappa_2$ &
                \includegraphics[width=0.3\textwidth]{pictures/d20-k2-II} &
                \includegraphics[width=0.3\textwidth]{pictures/d20-k2-CTriv}&
                \includegraphics[width=0.3\textwidth]{pictures/d20-k2-NV}\\ \hline
                $H$ &
                \includegraphics[width=0.3\textwidth]{pictures/d20-H-II} &
                \includegraphics[width=0.3\textwidth]{pictures/d20-H-CTriv}&
                \includegraphics[width=0.3\textwidth]{pictures/d20-H-NV}\\ \hline
                $G$ &
                \includegraphics[width=0.3\textwidth]{pictures/d20-G-II} &
                \includegraphics[width=0.3\textwidth]{pictures/d20-G-CTriv}&
                \includegraphics[width=0.3\textwidth]{pictures/d20-G-NV}\\ \hline
            \end{tabular}
        \end{center}
        \caption{Estimation of curvatures using Corrected Normal Current
        estimators \cite{lachaud:2022-dcg} for the shape ``Dice-20'' of Thingi10K
        database at resolution $256^3$. This estimator is
        parameterized by an input normal estimator: first column by
        ``Integral Invariant normals'' (radius $r=4.77$, second column
        by ``Convolved Trivial normals'' (radius $k=3$), third column
        by our presented normal estimator (radius $r=8.5$). Per row are displayed the
        estimated curvatures in order: first and second principal
        curvatures $\kappa_1$ and $\kappa_2$, mean curvature $H$,
            Gaussian curvature $G$. The range of curvature between deep
            blue and deep red is $\lbrack -0.1, 0.1 \rbrack$ with white
            color equal to $0$.}
    \end{figure}
